% \cleardoublepage{}
\clearpage{}
\begin{center}
    \bfseries \zihao{3} 摘~要
\end{center}

本生物化学实验课程项目式综合技能训练实验以蔗糖酶（EC 3.2.1.26）提取纯化、动力学分析与性质鉴定为主线，包含技术路线、绩效评估、动力学分析、性质鉴定四大板块，生动融合了各项现代生物化学实验的方法和手段，使得实验者能够熟练掌握生化实验技术操作规程和技能，整体了解科学研究项目的立题要求、路线规划、方法选择、方案设计和数据分析处理全流程。本文首先概述了实验的背景和总体设计，介绍了实验的方法、原理、材料、仪器和处理软件等内容。接着，按照实验步骤、实验数据处理和结果的顺序对本项目式综合技能训练实验中的蔗糖酶的分离与纯化、蛋白质浓度测定、酶活性的测定、蔗糖酶酶切去糖基化、正交试验探究最佳反应条件、SDS-PAGE、糖蛋白电泳、活性蛋白电泳、Western Blot、酶促反应动力学等十大板块进行了详细地分析。最后进行分析与讨论，系统地展示实验结果，总结不足并提出展望。

\vspace*{3em}

\textbf{关键词：}蔗糖酶；分离纯化；酶动力学；电泳；现代生物技术；生物化学实验
% \cleardoublepage{}
\clearpage{}
\begin{center}
    \bfseries \zihao{3} Abstract
\end{center}

This comprehensive skill training project of biochemistry laboratory course focuses on the extraction, purification, kinetic analysis, and characterization of sucrase(EC 3.2.1.26). It encompasses four major sections: technical procedures, performance evaluation, kinetic analysis, and property identification. The experiment vividly combines various methods and techniques of modern biochemistry experiments, enabling participants to proficiently master the operational procedures and skills of biochemical experiments. It provides an overall understanding of the entire process of formulating research project objectives, planning routes, selecting methods, designing plans, and analyzing and processing data.

The article begins by outlining the background and overall design of the experiment, introducing the methods, principles, materials, instruments, and processing software used. Subsequently, it meticulously analyzes ten major components of the project, including the separation and purification of sucrase, protein concentration determination, enzyme activity measurement, sucrase glycosylation, orthogonal experimental exploration of optimal reaction conditions, SDS-PAGE, glycoprotein electrophoresis, active protein electrophoresis, Western Blot, and enzyme-catalyzed reaction kinetics, following the sequence of experimental steps, data processing, and results.

In the final section, it conducts a thorough analysis and discussion, systematically presenting the experimental results, summarizing deficiencies, and proposing future prospects.

\vspace*{3em}

\textbf{Keywords:} Sucrase; Separation and purification; Enzyme kinetics; Electrophoresis; Modern biotechnology; Biochemical experiment